% Template for articles submitted to the International Journal of Forecasting
% Further instructions are available at www.ctan.org/pkg/elsarticle
% You only need to submit the pdf file, not the source files.
% If your article is accepted for publication, you will be asked for the source files.

\documentclass[11pt,3p,review,authoryear]{elsarticle}


\journal{International Journal of Forecasting}
\bibliographystyle{model5-names}
\biboptions{longnamesfirst}
% Please use \citet and \citep for citations.


\begin{document}

\begin{frontmatter}

\title{Post-Shock Volatility Forecasting Using Similarity-based Shock Aggregation}

  \author[uiuc]{David P. Lundquist}
   \ead{davidl11@illinois.edu}

 \author[uiuc]{Daniel J. Eck\corref{cor}}
 \address[uiuc]{Department of Statistics, University of Illinois at Urbana-Champaign\\
 605 E. Springfield Ave. Champaign, IL 61820}
 \ead{dje13@illinois.edu}
  \cortext[cor]{Corresponding author}


\begin{abstract}
 We develop a procedure for forecasting the volatility of a time series immediately following a news shock.  Adapting the similarity-based framework of Lin and Eck (2021), we exploit series that have experienced similar shocks.  We aggregate their shock-induced excess volatilities by positing the shocks to be affine functions of exogenous covariates.  The volatility shocks are modeled as random effects and estimated as fixed effects.  The estimates are then aggregated into a scalar quantity and used to adjust the GARCH volatility forecast of the time series under study by an additive term.  The adjusted and unadjusted forecasts are evaluated using the unobservable but easily-estimated realized volatility (RV). Numerical simulations are provided to illustrate conditions and hyperparameters under which our method thrives. A detailed real data application for forecasting volatility after the outcome of the 2016 United States presidential election demonstrates the applicability of the method.
\end{abstract}

\begin{keyword}
  Data Integration \sep 
 Prospective forecasting \sep 
 Risk reduction \sep 
Residual bootstrap \sep 
Cross validation 
\end{keyword}

\end{frontmatter}




\end{document}